Online {\IterComp}

### 2017-11-09 cgo18mscr.tex
changes to the result section; and other minor changes
Merged work and profiling. Many other changes
Switched template to PLDI 2018

\PassOptionsToPackage{table}{xcolor}

\documentclass[sigplan,10pt]{acmart}
\input{premable}

@@

\author{  }

%\author{Rodrigo C. O. Rocha}
%\affiliation{%
%  \institution{University of Edinburgh, UK}
%}
%\email{r.rocha@ed.ac.uk}

%\author{Pavlos Petoumenos}
%\affiliation{%
%  \institution{University of Edinburgh, UK}
%}
%\email{ppetoume@inf.ed.ac.uk}

%\author{Lu\'is F. W. G\'oes}
%\affiliation{%
%  \institution{PUC Minas, Brazil}
%}
%\email{lfwgoes@pucminas.br}

%\author{Murray Cole}
%\affiliation{
%  \institution{University of Edinburgh, UK}
%}
%\email{mic@inf.ed.ac.uk}

%\author{Zheng Wang}
%\affiliation{%
%  \institution{Lancaster University, UK}
%}
%\email{z.wang@lancaster.ac.uk}

%\author{Hugh Leather}
%\affiliation{%
%  \institution{University of Edinburgh, UK}
%}
%\email{hleather@inf.ed.ac.uk}

%\renewcommand{\shortauthors}{R. Rocha et al.}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10011007.10011006.10011041</concept_id>
%<concept_desc>Software and its engineering~Compilers</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%<concept>
%<concept_id>10011007.10011006.10011041.10011043</concept_id>
%<concept_desc>Software and its engineering~Retargetable compilers</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Software and its engineering~Compilers}
%\ccsdesc[500]{Software and its engineering~Retargetable compilers}
\keywords{{\IterComp}, Profiling} %, Relaxed Instrumentation}

@@

\input{intro}
\input{motivation}
\input{work}
\input{infra}
\input{prof}
\input{setup}
\input{results}
\input{related}
\input{conclusions}

>>>>

\PassOptionsToPackage{table}{xcolor}
\PassOptionsToPackage{draft}{hyperref}
\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\input{preamble}

@@

\author{Rodrigo C. O. Rocha}
\affiliation{
  \institution{University of Edinburgh, UK}
}
\email{r.rocha@ed.ac.uk}

\author{Pavlos Petoumenos}
\affiliation{
  \institution{University of Edinburgh, UK}
}
\email{ppetoume@inf.ed.ac.uk}

\author{Lu\'is F. W. G\'oes}
\affiliation{
  \institution{PUC Minas, Brazil}
}
\email{lfwgoes@pucminas.br}

\author{Murray Cole}
\affiliation{
  \institution{University of Edinburgh, UK}
}
\email{mic@inf.ed.ac.uk}

\author{Zheng Wang}
\affiliation{
  \institution{Lancaster University, UK}
}
\email{z.wang@lancaster.ac.uk}

\author{Hugh Leather}
\affiliation{
  \institution{University of Edinburgh, UK}
}
\email{hleather@inf.ed.ac.uk}

\renewcommand{\shortauthors}{R. Rocha et al.}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011041</concept_id>
<concept_desc>Software and its engineering~Compilers</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011041.10011043</concept_id>
<concept_desc>Software and its engineering~Retargetable compilers</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Compilers}
\ccsdesc[500]{Software and its engineering~Retargetable compilers}
\keywords{{\IterComp}, Profiling} %, Relaxed Instrumentation}

@@

\input{intro}
\input{motivation}
\input{work}
\input{infra}
%\input{prof}
\input{setup}
\input{results}
\input{related}
\input{conclusions}
